---
name: Kristina
surname: Gagalova, Ph.D.
position: "Research scientist"
address: "Genome Sciences Centre - Vancouver, Canada"
twitter: GagalovaK
github: KristinaGagalova
linkedin: kristina-gagalova
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "I am a Ph.D. graduate in Bioinformatics and I have pursued two Master's degrees in science. My research is focused in plant and evolutionary genomics. I have +3 years of work experience in industry and startups"
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Summary

 * Double academic curriculum with Master’s degrees in Bioinformatics and
Biotechnology. Solid basics in molecular biology and genetics
 * Deep understanding of bioinformatics algorithms and omics data analysis and multi-omics data analysis
 * Knowledge of classical and modern machine learning algorithms
 * Successfully completed a research-based Ph.D. in genomics, delivered with the publication of several peer-reviewed papers
 * Extensive collaboration with researchers from different scientific backgrounds
 * Successful project delivery in the context of omics research and data analysis
 

# Education and training

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Ph.D. doctorate - Bioinformatics", "2017-2022", "University of British Columnbia", "Vancouver, Canada",
  "Master of science - Bioinformatics", "2013-2015", "Vrije University", "Amsterdam, The Netherlands",
  "Master of science - Biotechnology", "2010-2013", "University of Bologna", "Bologna, Italy",
   "Bachelor of science - Biotechnology", "2007-2010", "University of Bologna", "Bologna, Italy",
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Work experience

```{r}
library(tibble)
tribble(
  ~Degree, ~Year, ~Institution, ~Where,
  "Research scientist", "Sep 2020 - Oct 2022", "Willow Biosciences Inc.", "Burnaby, Canada",
  "Data analyst", "Sep 2018 - Aug 2020", "BC Childrens Hospital", "Vancouver, Canada",
  "Bioinformatician", "Mar 2016 - Dec 2016", "GenomeScan", "Leiden, The Netherlands",
   "Data analyst", "Oct 2015 - Feb 2016", "MIMETAS", "Leiden, The Netherlands",
) %>% 
  detailed_entries(
    what=Degree, 
    when=Year,
    with=Institution, 
    where=Where
    )
```

# Awards and Fellowships

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  2018, "ECOSCOPE graduate trainee fellowship", "NSERC CREATE Graduate Training Program provides UBC graduate students with the skills needed to translate academic research into commercial and entrepreneurial activities",
  2017, "4YF - 4 years fellowship", "Four Year Doctoral Fellowship to support outstanding international students",
  2015, "Max Planck Institute and Erasmus+ fellowship", "Master's degree fellowship for international internship",
  2013, "VUFP-VU", "Vrije University fellowship for talented international students",
  2013, "University of Bologna: Mathematical, Physical, and Natural science traveling grant - in collaboration with the Rijksuniversiteit Groningen", "Master's degree fellowship for international internship",
  2013, "FindAMasters fellowship", "Biological Sciences Scholarship",
  2007, "ER.GO education grant", "Bachelor and Master's fellowship"
) %>% 
  brief_entries(
    Type,
    Year, 
    Desc
  )
```

# Publications

```{r}
library(dplyr)

options(encoding = "UTF-8")
scholar::get_publications("1claeqYAAAAJ") %>%
  distinct(title, .keep_all = TRUE) %>%
  transmute(bibtype = "Article", author = as.character(author),
            title = as.character(title),
            journaltitle = as.character(journal), year, key = row_number()) %>%
  RefManageR::as.BibEntry() %>%
  RefManageR::WriteBib("gagalova.bib")

bibliography_entries("gagalova.bib") %>%
 arrange(desc(issued))
```

